A finite-state morphological transducer for Kyrgyz

### 2011-10-14 dev/paper/paper.tex
minor fix
minor change
stupid subfigure stuff fixed
and moar paper!

@@

%FIXME: do we want this?
\subsection{Irregular [noun $+$ possessive $+$ case] forms}

@@

\begin{table}[htbp]
	\centering
	\caption{vowel harmony for archiphoneme \{I\}}\label{vowelharmonyI}
	\subfloat{
		\begin{tabular}{ll}
			\toprule
			after & result \\
			\midrule
			и & и \\
			ү & ү \\
			е & и \\
			ө & ү \\
			\bottomrule
		\end{tabular}
	}
	\qquad
	\subfloat{
		\begin{tabular}{ll}
			\toprule
			after & result \\
			\midrule
			ы & ы \\
			у & у \\
			а & ы \\
			о & у \\
			\bottomrule
		\end{tabular}
	}
\end{table}

@@

\begin{table}[htbp]
	\centering
	\caption{vowel harmony for archiphoneme \{A\}}\label{vowelharmonyA}
	\subfloat{
		\begin{tabular}{ll}
			\toprule
			after & result \\
			\midrule
			и & е \\
			ү & ө \\
			е & е \\
			ө & ө \\
			\bottomrule
		\end{tabular}
	}
	\qquad
	\subfloat{
		\begin{tabular}{ll}
			\toprule
			after & result \\
			\midrule
			ы & а \\
			у & а \\
			а & а \\
			о & о \\
			\bottomrule
		\end{tabular}
	}
\end{table}

@@

>>>>

% for glosses
\newcommand{\eng}[1]{`\textem{#1}'}

@@

%FIXME: do we want this?
\subsection{Irregular [noun + possessive + case] forms}

@@

\begin{table}[htbp]
	\centering
	\caption{vowel harmony for archiphoneme \{I\}}\label{vowelharmonyI}
	\subtable{
		\begin{tabular}{cc}
			\toprule
			after & result \\
			\midrule
			и & и \\
			ү & ү \\
			е & и \\
			ө & ү \\
			\bottomrule
		\end{tabular}
	}
	\hspace{2em}
	\subtable{
		\begin{tabular}{cc}
			\toprule
			after & result \\
			\midrule
			ы & ы \\
			у & у \\
			а & ы \\
			о & у \\
			\bottomrule
		\end{tabular}
	}
\end{table}

@@

\begin{table}[htbp]
	\centering
	\caption{vowel harmony for archiphoneme \{A\}}\label{vowelharmonyA}
	\subtable{
		\begin{tabular}{ll}
			\toprule
			after & result \\
			\midrule
			и & е \\
			ү & ө \\
			е & е \\
			ө & ө \\
			\bottomrule
		\end{tabular}
	}
	%\qquad
	\hspace{2em}
	\subtable{
		\begin{tabular}{ll}
			\toprule
			after & result \\
			\midrule
			ы & а \\
			у & а \\
			а & а \\
			о & о \\
			\bottomrule
		\end{tabular}
	}
\end{table}

@@

\begin{table}[htbp]
	\caption{examples comparing voicing and devoicing in Kyrgyz}\label{exvoicing}
	\subtable{
		\begin{tabular}{lll}
			\toprule
			underlying & surface & gloss \\
			\midrule
			/алма-DA/ & [алмада] & \eng{apple-LOC} \\
			/каз-DA/ & [казда] & \eng{goose-LOC} \\
			/баш-DA/ & [башта] & \eng{head-LOC} \\
			\bottomrule
		\end{tabular}
	}
	\hspace{2em}
	\subtable{
			\toprule
			underlying & surface & gloss \\
			\midrule
			/алма-GA/ & [алмага] & \eng{apple-DAT} \\
			/каз-GA/ & [казга] & \eng{goose-DAT} \\
			/баш-GA/ & [башка] & \eng{head-DAT} \\
			\bottomrule
	}
\end{table}

Here, the underlying /D/ is always realised as [д] when after a voiced segment (including a vowel), but is realised as [т] after an unvoiced consonant, while underlying /G/ is always realised as [г]\footnote{‹г› is pronounced [ɣ] in the context of front vowels and [ʁ] in the context of back vowels; it also has realisations of [g] and [ɢ] after nasals.} after a voiced segment, but is realised as [к]\footnote{‹к› is realised as [q] in the context of back vowels and [k] in the presence of front vowels.} after voiceless consonants.
